Time Stretching of the GeV Emission of GRBs: Fermi LAT data vs geometrical model

### 2014-03-23 Paper/gammaRays.tex
Drafted observation results

Out of 19 bursts studied, only 4 have at least 10 high energy events remaining after filtering, and thus eligible for the computation of stretching factors. The results of this computation are shown on figures \ref{fig:grb080916C}, \ref{fig:grb090510}, \ref{fig:grb090902B}, \ref{fig:grb090926A}.

\begin{figure}
        \centering
        \begin{subfigure}{0.49\textwidth}
                \includegraphics[width=\textwidth]{lightCurve080916C}
                \label{fig:lightCurve080916C}
        \end{subfigure}
        \begin{subfigure}{0.49\textwidth}
                \includegraphics[width=\textwidth]{probabilities080916C}
                \label{fig:probabilities080916C}
        \end{subfigure}
        \caption{080916C}
        \label{fig:grb080916C}
\end{figure}

\begin{figure}
        \centering
        \begin{subfigure}{0.49\textwidth}
                \includegraphics[width=\textwidth]{lightCurve090510}
                \label{fig:lightCurve090510}
        \end{subfigure}
        \begin{subfigure}{0.49\textwidth}
                \includegraphics[width=\textwidth]{probabilities090510}
                \label{fig:probabilities090510}
        \end{subfigure}
        \caption{090510}
        \label{fig:grb090510}
\end{figure}

\begin{figure}
        \centering
        \begin{subfigure}{0.49\textwidth}
                \includegraphics[width=\textwidth]{lightCurve090902B}
                \label{fig:lightCurve090902B}
        \end{subfigure}
        \begin{subfigure}{0.49\textwidth}
                \includegraphics[width=\textwidth]{probabilities090902B}
                \label{fig:probabilities090902B}
        \end{subfigure}
        \caption{090902B}
        \label{fig:grb090902B}
\end{figure}

\begin{figure}
        \centering
        \begin{subfigure}{0.49\textwidth}
                \includegraphics[width=\textwidth]{lightCurve090926A}
                \label{fig:lightCurve090926A}
        \end{subfigure}
        \begin{subfigure}{0.49\textwidth}
                \includegraphics[width=\textwidth]{probabilities090926A}
                \label{fig:probabilities090926A}
        \end{subfigure}
        \caption{090926A}
        \label{fig:grb090926A}
\end{figure}

\begin{table}
	\centering
	\small
	\begin{tabular}{ l | S[table-format=2.3]@{\; -- \;}S[table-format=2.3] | S[table-format=2.3]@{\; -- \;}S[table-format=2.3] | S[table-format=2.3]@{\; -- \;}S[table-format=2.3] | S[table-format=2.3]@{\; -- \;}S[table-format=2.3] | S[table-format=2.3]@{\; -- \;}S[table-format=2.3] }
		\multicolumn{1}{ c |}{GRB} & \multicolumn{2}{ c |}{$1\sigma$} & \multicolumn{2}{ c |}{$2\sigma$} & \multicolumn{2}{ c |}{$3\sigma$} & \multicolumn{2}{ c |}{$4\sigma$} & \multicolumn{2}{ c }{$5\sigma$} \\
		\hline
		080825C	&	1.04  & 2.24	&	0.67 & 3.32	&	0.42 & 5.83	&	0.19 & 14.9		&	0.087 & 35.7	\\
		090501	&	0.58  & 1.1		&	0.43 & 1.61	&	0.32 & 2.29	&	0.22 &  3.03	&	0.17  &  5.11	\\
		090902B	&	0.629 & 0.635	&	0.36 & 0.89	&	0.23 & 1.57	&	0.13 &  2.87	&	0.084 &  4.56	\\
		090926A &	2.61  & 3.33	&	1.99 & 6.62	&	1.34 & 9.15	&	0.73 & 13.5		&	0.48  & 19.4
	\end{tabular}
	\caption{Caption}
	\label{tab:observationResults}
\end{table}

>>>>

Out of 19 bursts studied, only 4 have at least 10 high energy events remaining after filtering, and thus eligible for the computation of stretching factors. The results of this computation are shown on figures \ref{fig:grb080916C}, \ref{fig:grb090510}, \ref{fig:grb090902B}, \ref{fig:grb090926A} and table \ref{tab:observationResults}.

Out of these 4 bursts, two (080916C and 090510) have stretching factors compatible with $\kappa = 1$ within $2\sigma$ range.

GRB 090926A has, however, high energy radiation stretched with respect to low energy signal (that is $\kappa > 1$). In contrast to that, GRB 090902B has low energy radiation stretched with respect to high energy signal ($\kappa < 1$).

So we obtained a preliminary (for significance is less than $5\sigma$) result that the stretching factors for observable bursts might be both larger and smaller than $1$.

\begin{figure}
        \centering
        \begin{subfigure}{0.49\textwidth}
                \includegraphics[width=\textwidth]{lightCurve080916C}
                \label{fig:lightCurve080916C}
        \end{subfigure}
        \begin{subfigure}{0.49\textwidth}
                \includegraphics[width=\textwidth]{probabilities080916C}
                \label{fig:probabilities080916C}
        \end{subfigure}
        \caption{GRB 080916C results. Stretching factor is compatible with $\kappa = 1$ within $2\sigma$.}
        \label{fig:grb080916C}
\end{figure}

\begin{figure}
        \centering
        \begin{subfigure}{0.49\textwidth}
                \includegraphics[width=\textwidth]{lightCurve090510}
                \label{fig:lightCurve090510}
        \end{subfigure}
        \begin{subfigure}{0.49\textwidth}
                \includegraphics[width=\textwidth]{probabilities090510}
                \label{fig:probabilities090510}
        \end{subfigure}
        \caption{GRB 090510 results. Stretching factor is compatible with $\kappa = 1$ within $1\sigma$.}
        \label{fig:grb090510}
\end{figure}

\begin{figure}
        \centering
        \begin{subfigure}{0.49\textwidth}
                \includegraphics[width=\textwidth]{lightCurve090902B}
                \label{fig:lightCurve090902B}
        \end{subfigure}
        \begin{subfigure}{0.49\textwidth}
                \includegraphics[width=\textwidth]{probabilities090902B}
                \label{fig:probabilities090902B}
        \end{subfigure}
        \caption{GRB 090902B results. Low energy radiation is stretched ($\kappa < 1$) with significance of $2\sigma$.}
        \label{fig:grb090902B}
\end{figure}

\begin{figure}
        \centering
        \begin{subfigure}{0.49\textwidth}
                \includegraphics[width=\textwidth]{lightCurve090926A}
                \label{fig:lightCurve090926A}
        \end{subfigure}
        \begin{subfigure}{0.49\textwidth}
                \includegraphics[width=\textwidth]{probabilities090926A}
                \label{fig:probabilities090926A}
        \end{subfigure}
        \caption{GRB 090926A results. High energy radiation is stretched ($\kappa > 1$) with significance of $3\sigma$.}
        \label{fig:grb090926A}
\end{figure}

\begin{table}
	\centering
	\small
	\begin{tabular}{ l | S[table-format=2.3]@{\; -- \;}S[table-format=2.3] | S[table-format=2.3]@{\; -- \;}S[table-format=2.3] | S[table-format=2.3]@{\; -- \;}S[table-format=2.3] | S[table-format=2.3]@{\; -- \;}S[table-format=2.3] | S[table-format=2.3]@{\; -- \;}S[table-format=2.3] }
		\multicolumn{1}{ c |}{GRB} & \multicolumn{2}{ c |}{$1\sigma$} & \multicolumn{2}{ c |}{$2\sigma$} & \multicolumn{2}{ c |}{$3\sigma$} & \multicolumn{2}{ c |}{$4\sigma$} & \multicolumn{2}{ c }{$5\sigma$} \\
		\hline
		080825C	&	1.04  & 2.24	&	0.67 & 3.32	&	0.42 & 5.83	&	0.19 & 14.9		&	0.087 & 35.7	\\
		090501	&	0.58  & 1.1		&	0.43 & 1.61	&	0.32 & 2.29	&	0.22 &  3.03	&	0.17  &  5.11	\\
		090902B	&	0.629 & 0.635	&	0.36 & 0.89	&	0.23 & 1.57	&	0.13 &  2.87	&	0.084 &  4.56	\\
		090926A &	2.61  & 3.33	&	1.99 & 6.62	&	1.34 & 9.15	&	0.73 & 13.5		&	0.48  & 19.4
	\end{tabular}
	\caption{Burst observation results. Ranges of allowed stretching factors are shown for studied bursts for multiple levels of significance.}
	\label{tab:observationResults}
\end{table}
